---
title: "p8105_hw5_sp4170"
author: "Shihui Peng"
date: "2023-11-15"
output: github_document
---
load package and set seed for reproducibility
```{r, echo=FALSE, message=FALSE}
library(tidyverse)
set.seed(1)
```


# problem 2

## data import

```{r}
file_import_df = 
  tibble(
    file_name = list.files(path = 'data/'),
    path = str_c('data/', file_name)
  ) |> 
  mutate(
    data = map(path, read_csv)
  ) |> 
  unnest(data)
```
* i create a df named 'file_import_df', make a tibble consisted of every file's name and their relative path. i use `mutate()` to create a new variable 'data', which contain every csv file i imported using `map()` function. I use `unnest()` to unnest contents of each cell of variable data.

## data tidy

```{r}
file_tidy_df = 
  file_import_df |> 
  janitor::clean_names() |> 
  separate(file_name, c('arm', 'subject_id'), sep = '\\_') |> 
  select(-path) |> 
  mutate(
    subject_id = str_remove(subject_id, '\\.csv'),
    arm = ifelse(arm == 'con', 'control', 'experience')
  ) |> 
  pivot_longer(
    week_1 : week_8,
    names_to = 'observation_time',
    values_to = 'value',
    names_prefix = 'week_'
  ) |> 
  mutate(
    observation_time = as.numeric(observation_time)
  )
```
* i tidy the result:
  * i use `separate()` to create variable 'arm' and 'subject_id'. i remove column 'path' as it is not needed. i mutate variable subject_id by deleting the suffix and variable arm by renaming 'con' as 'control' and 'exp' as 'experience'. I tidy cols week_1 to week_8 and create col 'observation_time' indicating weeks for each observation time point and col 'value' for each value. i change the data type of variable observation_time from character type to numeric type.
